Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence

### 2020-07-15 drafts/outline.tex
editing methods sect.

@@

Particle capture in transitionally turbulent flows (\(1<\Rey<1000\)), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter (\(d_p\)), derived for creeping flow. Hence, empirical estimates must be used. \citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).

@@

Our experiment was conducted in a recirculating flume. Water was propelled by an electric pump through a rectangular pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity), through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure XY). In the upper range of the pump's span, cavitation (i.e., taking on air bubbles) occured, which was accompanied by a distinct noise. By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump chambers stayed free of cavitation up to a rotation speed well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.

@@

We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel. The perforated top of the array gaps between the array and the upstream and downstream edges of the well were covered with flat, rectangular pieces of aluminum secured with

\begin{figure}[h]
\includegraphics[width=10cm]{wf5-200sizedist.png}
\centering
\caption{Walnut shell particle size distribution (TODO: caption)}
\end{figure}

@@

TODO\\
\hfill\break
The assumption that probability of retention (\(p_r\)) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased \(\eta\prime\) in comparison to greased dowels. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter (\(d_c\)). However, with our model for Reynolds number (\(\Rey_c \propto d_c\)), and both us and \citet{Fauria_2015} finding \(\eta\prime \sim -\Rey_c\), increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.

>>>>

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

@@

Particle capture in transitionally turbulent flows (\(1<\Rey<1000\)), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter (\(d_p\)), derived for creeping flow. Hence, empirical estimates must be used. \citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)). \(C\), \(a\), and \(b\) are empirically determined regression coefficients.

@@

Our experiment was conducted in a recirculating flume. Water was propelled by an electric pump through a rectangular pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity), through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure XY). In the upper range of the pump's span, cavitation (i.e., taking on air bubbles) occured, which was accompanied by a distinct noise. By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.

@@

We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel. The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream and downstream edges of the well were covered with attached, flat, rectangular pieces of aluminum in order to avoid irregularities in the channel's cross-sectional shape. Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.

\begin{figure}[h]
\includegraphics[width=10cm]{wf5-200sizedist.png}
\centering
\caption{Walnut shell particle size distribution (TODO: caption, crop out previous caption)}
\end{figure}

@@

The assumption that probability of retention (\(p_r\)) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased \(\eta\prime\) in comparison to greased dowels. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter (\(d_c\)). However, with our model for Reynolds number (\(\Rey_c \propto d_c\)), and both us and \citet{Fauria_2015} finding \(\eta\prime \sim -\Rey_c\), increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
